%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Eunika Wu - Resume
% 10/04/2019

\documentclass[]{hieudo-build}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eunika Wu}
{\urlstyle{same}
	\ci{\faAt} \href{mailto:eunikawu@gmail.com}{ eunikawu@gmail.com } 
	\par
    \ci{\faGlobe} \href{https://nikawu.eu}{ nikawu.eu } \par
	\ci{\faGithub} \href{https://github.com/DED8IRD}{ github.com/DED8IRD } 
	\par
	\ci{\faLinkedinSquare} \href{https://www.linkedin.com/in/eunika-wu/}{ linkedin.com/in/eunika-wu }
	\par
} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.62\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{PDX Code Guild}{Mar 2018 - Current} \\
\position{Dev Bootcamp Instructor}{Portland, OR}
\vspace{\topsep}
\begin{tightemize}
\item Instructed, designed, and updated curriculum to the Python Full Stack Bootcamp (Python/Django, Vue) and the MERN Stack course (MongoDB, Express, React, Node). \\
\smallskip
\end{tightemize}
\sectionsep

\workplace{Omari.io}{Mar 2015 - Jun 2019} \\
\position{Web Developer \&  UX Researcher}{Santa Cruz, CA}
\begin{tightemize}
\item Conducted usability research on NodingBat, an open source JavaScript coding school written in Meteor.js, and applied UX optimizations that improved user workflow by 200\% \\
\item Made error feedback more responsive in the live-coding app, and added debug tools to lower barriers of entry to NodingBat's primary user base.
\end{tightemize}
\sectionsep

\workplace{UC Santa Cruz - HCI Lab}{Jun 2017 – Nov 2017} \\
\position{Lead Data Visualization Engineer}{Santa Cruz, CA}
\begin{tightemize}
\item Created web app providing D3 visualizations for long-term cognitive behavioral therapy data, using NLTK and LIWC to illustrate the linguistic patterns of depression.  \\
\item Guided final decisions on natural language processing \& design.
\end{tightemize}
\sectionsep
\position{Android Developer \& Researcher}{Sept 2016 – Jul 2017}
\begin{tightemize}
\item Developed GSR signal processing mobile app  critical in the deployment of a study testing how framing can skew how we interpret realtime biofeedback on our emotional state. \\
\item Coauthored paper detailing this study's findings published in the ACM (2018).
\end{tightemize}
\sectionsep

\workplace{Xactly Corp}{Jan 2017 - Jun 2017} \\
\position{Software Engineer (Externship)}{San Jose, CA}
\begin{tightemize}
\item Developed data visualization dashboard using Node/React \& Java/Spring that improved and replaced the prior diagnostics toolset for Xactly's internal support team.
\end{tightemize}
\sectionsep

% \workplace{BubbleTea Time Co.}{Jun 2013 - Aug 2014} \\
% \position{Manager}{San Marcos, CA}
% \begin{tightemize}
% \item Oversaw employee training \& orienting, scheduling, inventory, daily accounting, and customer service.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\workplace{University of California at Santa Cruz}{Graduated Sept 2017} \\
\smallskip
\position{B.A. in Computer Science}{\it{Cum Laude - 3.79}}
\position{B.S. in Cognitive Science}{\it{Summa Cum Laude - 3.92}}
\smallskip
\position{\small{AI/HCI Concentration}}{Cumulative GPA: Cum Laude - 3.80}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\runsubsection{D.A.V.E}
\descript{Screenplay bot}
\normalsize Generates properly formatted bot-
generated screenplays. Available as standalone PyPI package or web app deployed as a Dockerized EC2 instance. \\
% \techstack{Built with Python, Django, React, NLTK} \\
\sectionsep

\runsubsection{Red}
\descript{Natural Language Processing Q\&A Module}
\normalsize Ask a question about a body of text and receive an answer generated from semantic dependency graphs connecting entities to others and actions. \\
% \techstack{Built with Python, NLTK}
\sectionsep

\runsubsection{D2D}
\descript{Nudity Filter}
\normalsize Autodetects nudity using TensorFlow \& OCV and replaces image with duck, allowing freedom of choice to uncover, and freedom from unsolicited nudes.\\
% \techstack{Built with OCV, TensorFlow}
\sectionsep

\runsubsection{SENTIENCE}
\descript{Meme bot}
\normalsize Generates OC from pages of the Weird Facebook collective using Markov chains for text and Pillow to generate images. \\
% \techstack{Built with Python, Web2py, Vue.js, NLTK, Pillow} \\
\sectionsep 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}
\begin{flushleft}
\narrower
\runsubsection{Languages:} 
\smallskip \\
\normalsize
  Fluent: Python, JavaScript, Java \\
  Familiar: TypeScript, C++, C \\
  Learning: C\#, Dart (Flutter)
\sectionsep

\runsubsection{Backend:}
\normalsize
  Django, Flask, Web2py, Node, Express, Spring
\sectionsep

\runsubsection{Frontend:}
\normalsize
  React, Vue, jQuery, \\
  HTML5, CSS3, SASS/LESS, Responsive Design
\sectionsep

\runsubsection{Databases:}
\normalsize
  Postgres, MySQL, Oracle, MongoDB, GraphQL
\sectionsep

\runsubsection{Deployment:}
\normalsize
  AWS (EB, EC2, S3), Heroku, PythonAnywhere
\sectionsep

\runsubsection{Tools:}
\normalsize
  Git, Webpack, Docker,
  Android Studio, 
  NLTK, SpaCy, TensorFlow, OCV, 
  Blender, 
  Adobe Illustrator \& Photoshop
\sectionsep

% \runsubsection{Environments:}
% \normalsize
%   Windows, Linux/Unix
  
\end{flushleft}
% \sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     COURSEWORK
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Coursework}
% Algorithms \& ADTs, Data Structures, Computability, Databases, Web Apps, Software Engineering,
% Artificial Intelligence, Natural Language Processing, Human Factors, HCI/UX, Human-Robot Interaction, Universal Access
% \sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% Dean's List \\
% Da Vinci Scholar
% \sectionsep

\end{minipage} 
\hfill

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     Publications
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \descript{Hollis, V., Pekurovsky, A., \textbf{Wu, E.}, and Whittaker, S. 2018. On Being Told How We Feel: How Algorithmic
% Sensor Feedback Influences Emotion Perception. Proc. ACM Interact. Mob. Wearable Ubiquitous Technol. 2, 3, Article 01}

% \begin{flushright}
% \DTMsetdatestyle{mylastupdate}
% \DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}
% \end{flushright}

\end{document}  
